```{r, echo=FALSE}
source('report-fun.R')
```

# Report for study: `r .study`

## Contact Information

**Data contributor:** `r .dat$contacts$name`.

**Email:** `r .dat$contacts$email`.

**Address:** `r .dat$contacts$address`.

## Citation
Information about the primary reference for the data you provided.

**Reference:** `r .dat$references$citation`

**DOI:** `r  bibGetElement(.dat$bib, element = "doi")`

**Abstract:** `r  bibGetElement(.dat$bib, element = "abstract")`

## Overview of data provided

Data for `r length(.dat$data$studyName)` individuals from `r length(unique(.dat$data$location))` locations covering `r length(unique(.dat$data$species))` species.

The dataset includes `r length(unique(.dat$data$species))` species belonging to `r length(unique(.dat$data$family))` family(ies), presenting `r length(unique(.dat$data$pft))` functional type(s), growing in `r length(unique(.dat$data$growingCondition))` condition(s) within `r length(unique(.dat$data$vegetation))` major type(s) of habitat:


### Number of records for each variable

```{r echo=FALSE, comment='',results='asis'}
counts  <-  apply(!is.na(.dat$data), MARGIN=2, FUN = sum)
counts  <-  counts[counts>0]  #only include no zeros
counts  <-  counts[names(counts)%in%.dat$dictionary$Variable[.dat$dictionary$Group=="tree"]]
kable(cbind(counts))
```


## Study details

### Location

**Location data**
```{r echo=FALSE, message=FALSE, warning=FALSE, comment='',results='asis'}
options(width =160)
kable(locLevelInfo(.dat$data))
```

**Global map**

```{r echo=FALSE, fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
prepdata  <-  prepMapInfo(alldata$data, .study)
drawWorldPlot (prepdata)
```

**Country map**

```{r echo=FALSE, fig.width=8, fig.height=6, message=FALSE, warning=FALSE}
repMissingInfo(prepdata)
drawCountryPlot(prepdata)
```

**Stand description**
Information about the growing condition of plants in your study, i.e. their local environment.

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
kable(standLevelInfo(.dat$data))
```

### Species data

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='',results="asis"}
kable(spLevelInfo(.dat$data))
```

### Methods
```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
metaTable  <-  getMeta(.study)
writeLines(paste0(metaTable[,1], ": ", metaTable[,2], "\n"))
```

## Plots of data

This is how the study `r .study` (each colour represents a species) fits in the entire dataset (grey).

```{r fig.height=8, fig.width=8, echo=FALSE, warning=FALSE, message=FALSE}
makePlotPanel(alldata, .dat)
```
